---
title: "Assignment 3"
author: "Rachana"
date: "2022-10-18"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#loading library functions
library(caret)
library(e1071)
```
```{r}
# reading csv file
UniversalBank = read.csv("UniversalBank.csv")
data=UniversalBank
head(UniversalBank)

```

```{r}
#Coverting data to factor variables

data$Personal.Loan=as.factor(data$Personal.Loan)
data$Online=as.factor(data$Online)
data$CreditCard=as.factor(data$CreditCard)
```
```{r}
#splitting data into 60:40 ratio

set.seed(280)

split=createDataPartition(data$Personal.Loan,p=0.6,list=FALSE,times=1)
train_data=data[split,]
valid_data=data[-split,]
head(train_data)
```

```{r}
#Normalizing the data

normalized=preProcess(train_data[,-c(10,13,14 )])
train_normalized<-predict(normalized,train_data)

head(train_normalized)
```

#A:Creating a pivot table with  online  as coloumn and credit card as row and 
#Personal loan as secondary row
```{r}
table_A<-table(train_normalized$CreditCard,train_normalized$Personal.Loan,train_normalized$Online)
prop1<-prop.table(table_A)
View(prop1)
View(table_A)
```
#the probability that the customer will accept the loan offer  given that he is having a bank credit card (CC = 1) and being an active user of online banking services (Online =1) 
                                                                                  

#B: P(loan=1/(cc=1,online=1))=52/(52+446) = 0.1044
 
#C1: Pivot table with loan as row funtion and online as coloumn function

```{r}  
table_C1<-table(train_normalized$Personal.Loan,train_normalized$Online)
View(table_C1)
```

#C2: Pivot table with loan as row function  and creditcard as coloumn function

```{r}
table_C2<-table(train_normalized$Personal.Loan,train_normalized$CreditCard)
View(table_C2)
```

#Creating table for loan=1
```{r}
table_C3<-table(train_normalized$Personal.Loan)
View(table_C3)
prop<-prop.table(table_C3)
View(prop)
```
#D: computing the given probabilities

#i. P(CC = 1 | Loan = 1) (the proportion of credit card holders among the loan acceptors) =93/288=0.3229166


#ii. P(Online = 1 | Loan = 1)= 175/288=0.607


#iii. P(Loan = 1) (the proportion of loan acceptors)  =288/3000=0.096


#iv. P(CC = 1 | Loan = 0)  =764/2712=0.2817


#v. P(Online = 1 | Loan = 0) =1583/2712=0.58370   


#vi. P(Loan = 0) =2712/3000=0.904


#E : Computing NAIVE BAYES PROBABLITY: P(Loan=1|CC=1,Online=1)=0.1209


#F:Values obtained from pivot table(B) is more accurate and precise than E
#since they are calculated based on count or frequency directly from
#the table

#G :Running Naive Bayes Probability
```{r}
model<-naiveBayes(Personal.Loan~CreditCard+Online,data=train_normalized)
model
```

# comparing naviebayes probability of manual calculations error and runoff error,Naive Bayes probablity is more accurate as the manually calculated values might have calculation errors.


